Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population

### 2022-10-15 src/tex/appendicies.tex
rewrite weird sentence

Another important feature of basis splines is that under appropriate prior conditions, one can alleviate sensitivities to arbitrarily 
chosen prior specifications that splines commonly struggle with. Previous studies using splines had to perform multiple analyses, varying the 
number of spline knots, then either marginalized over the models or used model comparisons to motivate the best choice \citep{Edelman_2022ApJ}. 
We can avoid this step with the use of penalized splines (or P-Splines) \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
where one adds a smoothing prior comprised of Gaussian distributions on the differences between neighboring basis spline coefficients. 
This prior allows one to populate the domain more densely with knots without the worry of extra variance in the inferred spline functions. When also fitting the scale 
of the smoothing prior (i.e. the width of the Gaussian distributions on the differences), this allows the data to inform the scale of smoothing required. 
We discuss the details of our smoothing prior implementation in more detail in the next section, Appendix \ref{sec:psplines}, 
along with our specific prior and basis choices for each model following that in Appendix \ref{sec:modelpriors}.

>>>>

Another important feature of basis splines is that under appropriate prior conditions, one can alleviate sensitivities to arbitrarily 
chosen prior specifications that splines commonly struggle with. Previous studies using splines had to perform multiple analyses, varying the 
number of spline knots, then either marginalized over the models or used model comparisons to motivate the best choice \citep{Edelman_2022ApJ}. 
We can avoid this step with the use of penalized splines (or P-Splines) \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
where one adds a smoothing prior comprised of Gaussian distributions on the differences between neighboring basis spline coefficients. 
This allows for knots to be densely populated across the domain without the worry of extra variance in the inferred spline functions. 
When also fitting the scale of the smoothing prior (i.e. the width of the Gaussian distributions on the differences), the data will inform the model 
of the preferred the scale of smoothing required. We discuss the details of our smoothing prior implementation in more detail in the next section, 
Appendix \ref{sec:psplines}, following with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.
